### 2020-09-23 LaTeX/sections/appendix.tex
appendix

\section{Extended discussion on cleaning up data structures}

@@

>>>>

\section{Clearing storage (extended discussion)}

@@

\section{Collateralization options}

In \cm, both the tokens and ETH that a trader want to potentially use in the order book are pre-loaded into the contract. Consider Alice who holds a token and decides she wants to trade it for ETH. In this model, she must first transfer the tokens to the contract and then submit an ask order. If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert. If she waits for confirmation, this introduces a delay. This delay seems reasonable but we point out a few ways it could be addressed:

\item \textbf{Use \texttt{msg.value}.} For the ETH side of a trade (\ie for bids), ETH could be sent with the function call to \texttt{submitBid()} to remove the need for \texttt{depositEther()}.

\item \textbf{asdf} \cm could

\item \textbf{asdf} \cm could

\item \textbf{asdf} \cm could

\item \textbf{asdf} \cm could

%% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
%\subsection{Collateralization}
%
%Options for non-collateralized markets
%ERC20 to ERC20 -> extra transaction
%
